A pipeline to analyse time-course gene expression data

### 2020-07-15 scripts/manuscript.Rmd
finish initial switch to new Moanin class

```{r assigning_scores_and_labels}
# Then assign scores and labels to all the data, using a goodness-of-fit
# scoring function.
scores_and_labels = splines_kmeans_score_and_label(
    moanin_model, kmeans_clusters)
```

@@

both_labels = data.frame("kmeans"=kmeans_labels, "scored"=labels)
# Create another cluster.
#both_labels[is.na(both_labels)] = 21
confusion_matrix = table(both_labels)
text = as.matrix(as.character(confusion_matrix))
dim(text) = dim(confusion_matrix)
aheatmap(confusion_matrix, treeheight=0, main="Confusion matrix", 
	      border_color="black", txt=text, legend=FALSE, Rowv=NA,
	      Colv=NA, sub="Goodness-of-fit assignments")
labels = scores_and_labels$labels
labels = unlist(labels[!is.na(labels)])

@@

```{r topScoreInCluster2, fig.height=6, fig.width=6, fig.cap=paste("Top scoring genes in Cluster",cluster_of_interest)}
# order them by their score in cluster
ord = order(scores_and_labels$scores[genes_in_cluster2,
                     cluster_of_interest])
cluster2Score = genes_in_cluster2[ord]
dataToPlot = rbind([cluster2Score[1:4], ],
    "Centroid"=kmeans_clusters$centroids[cluster_of_interest, ])
plot_splines_data(moanin_model, data=dataToPlot, 
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    mar=c(1.5,2.5,2,0.1))
```

@@

res = aheatmap(
    assay(de_moanin_model[genes_to_plot,ord]),
    Colv=NA,
    color="YlGnBu",
    annCol=submeta[,
                c("Group", "Timepoint")],
    annLegend=FALSE,
    annColors=ann_colors,
    main=paste("Cluster", cluster_to_plot, "(raw)"),
    treeheight=0, legend=FALSE)

# Now use the results of the previous call to aheatmap to reorder the genes.
aheatmap(
    rescale_values(de_moanin_model[genes_to_plot,ord])[res$rowInd,],
    Colv=NA,
    Rowv=NA,
    annCol=submeta[,
                c("Group", "Timepoint")],
    annLegend=TRUE,
    annColors=ann_colors,
    main=paste("Cluster", cluster_to_plot, "(rescaled)"),
    treeheight=0)

@@

i = 1
for(n_cluster in all_possible_n_clusters){
    clustering_results = splines_kmeans(y,
	    n_clusters=n_cluster, random_seed=42,
	    n_init=10)
    wss_values[i] = sum(clustering_results$WCSS_per_cluster)
    all_clustering[[i]] = clustering_results$clusters
    i = i + 1
}
```

@@

```{r}
n_genes = dim(y)[1]
indices = sample(1:dim(y)[1], n_genes, replace=TRUE)

bootstrapped_y = y[indices, ]
```

@@

```{r}
subsample_proportion = 0.8
indices = sample(1:dim(y)[1], n_genes * subsample_proportion, replace=FALSE)

subsampled_y = y[indices, ]
```

@@

```{r bootstrapped_clustering, eval=FALSE}
# You may want to set the random seed of the experiment so that the results
# don't vary if you rerun the experiment.
# set.seed(random_seed)
n_genes = dim(y)[1] * sample_proportion
indices = sample(1:dim(y)[1], n_genes, replace=TRUE)

random_subsample_y = y[indices, ]
kmeans_clusters = splines_kmeans(y[indices,]
    random_subsample_y, splines_model, n_clusters=n_clusters,
    random_seed=random_seed,
    n_init=20)

>>>>

```{r assigning_scores_and_labels}
# Then assign scores and labels to *all* the data, using a goodness-of-fit
# scoring function.
scores_and_labels = splines_kmeans_score_and_label(
    moanin_model, kmeans_clusters)
```

@@

both_labels = data.frame("kmeans"=kmeans_labels, "scored"=labels)
# Create another cluster.
#both_labels[is.na(both_labels)] = 21
confusion_matrix = table(both_labels)
text = as.matrix(as.character(confusion_matrix))
dim(text) = dim(confusion_matrix)
aheatmap(confusion_matrix, treeheight=0, main="Confusion matrix", 
	      border_color="black", txt=text, legend=FALSE, Rowv=NA,
	      Colv=NA, sub="Goodness-of-fit assignments")

# recreate, so in same order, etc as before
labels = scores_and_labels$labels
labels = unlist(labels[!is.na(labels)])

@@

```{r topScoreInCluster2, fig.height=6, fig.width=6, fig.cap=paste("Top scoring genes in Cluster",cluster_of_interest)}
# order them by their score in cluster
ord = order(scores_and_labels$scores[genes_in_cluster2,
                     cluster_of_interest])
cluster2Score = genes_in_cluster2[ord]
dataToPlot = rbind(assay(moanin_model[cluster2Score[1:4], ]),
    "Centroid"=kmeans_clusters$centroids[cluster_of_interest, ])
plot_splines_data(moanin_model, data=dataToPlot, 
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    mar=c(1.5,2.5,2,0.1))
```

@@

res = aheatmap(
    assay(moanin_model[genes_to_plot,ord]),
    Colv=NA,
    color="YlGnBu",
    annCol=submeta[,
                c("Group", "Timepoint")],
    annLegend=FALSE,
    annColors=ann_colors,
    main=paste("Cluster", cluster_to_plot, "(raw)"),
    treeheight=0, legend=FALSE)

# Now use the results of the previous call to aheatmap to reorder the genes.
aheatmap(
    rescale_values(moanin_model[genes_to_plot,ord])[res$rowInd,],
    Colv=NA,
    Rowv=NA,
    annCol=submeta[,
                c("Group", "Timepoint")],
    annLegend=TRUE,
    annColors=ann_colors,
    main=paste("Cluster", cluster_to_plot, "(rescaled)"),
    treeheight=0)

@@

i = 1
for(n_cluster in all_possible_n_clusters){
    clustering_results = splines_kmeans(de_moanin_model,
	    n_clusters=n_cluster, random_seed=42,
	    n_init=10)
    wss_values[i] = sum(clustering_results$WCSS_per_cluster)
    all_clustering[[i]] = clustering_results$clusters
    i = i + 1
}
```

@@

```{r}
n_genes = dim(y)[1]
indices = sample(1:dim(de_moanin_model)[1], n_genes, replace=TRUE)

bootstrapped_y = de_moanin_model[indices, ]
```

@@

```{r}
subsample_proportion = 0.8
indices = sample(1:dim(de_moanin_model)[1], n_genes * subsample_proportion, replace=FALSE)

subsampled_y = de_moanin_model[indices, ]
```

@@

```{r bootstrapped_clustering, eval=FALSE}
# You may want to set the random seed of the experiment so that the results
# don't vary if you rerun the experiment.
# set.seed(random_seed)
n_genes = dim(de_moanin_model)[1] * sample_proportion
indices = sample(1:dim(de_moanin_model)[1], n_genes, replace=TRUE)

kmeans_clusters = splines_kmeans(de_moanin_model[indices,]
    n_clusters=n_clusters,
    random_seed=random_seed,
    n_init=20)
